Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-26 paper/main.tex
A_u, A_phi

In \autoref{eq:artist:morphism-of-sheaf-data}, $\dfuncc$ was introduced as a morphism between sheaf functors $\sheafc^{\vindex^*}$. Since the artist is a functor $\vartist: \sheafc^{\vindex^*} \rightarrow \sheaf_{\vartist}$, it follows from \autoref{eq:related-work:equivariance:functor_diagram} that 
\begin{equation}
  \begin{tikzcd}
    \sheafc_{\vindex^{*}} \arrow[d, "\dfuncc"'] \arrow[r, "\vartistc"] & \sheafc_{\vartist} \arrow[d, "\dfuncc^{\prime} \coloneqq\vartist(\dfuncc)"] \\
    \sheafc_{\vindex^{*}} \arrow[r, "\vartistc"']                      & \sheafc_{\vartist}                                                         
    \end{tikzcd}
\end{equation}
an arbitrary morphism $\dfunc$ on the data sheaf has a compatible morphism $\dfunc^{\prime}$ on the graphic sheaf.

>>>>

In \autoref{eq:artist:morphism-of-sheaf-data}, $\dfuncc$ was introduced as a morphism between sheaf functors $\sheafc^{\vindex^*}$. Since the artist is a functor $\vartist: \sheaf^{\vindex^*} \rightarrow \sheaf_{\vartist}$, it follows from \autoref{eq:related-work:equivariance:functor_diagram} that 
\begin{equation}
  \begin{tikzcd}
    \sheafc_{\vindex^{*}} \arrow[d, "\dfuncc"'] \arrow[r, "\vartistc"] & \sheafc_{\vartist} \arrow[d, "\dfuncc^{\prime} \coloneqq\vartist(\dfuncc)"] \\
    \sheafc_{\vindex^{*}} \arrow[r, "\vartistc"']                      & \sheafc_{\vartist}                                                         
    \end{tikzcd}
\end{equation}
an arbitrary morphism $\dfunc$ on the data sheaf has a compatible morphism $\dfunc^{\prime}$ on the graphic sheaf.
